Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-05-17 background.tex
2015.05.16 (Alex & Vassilis) Extensive re-wording throughout the paper. Abstract on its one file. Better figure scaling and alignment. Re-ordering of algorithms in the histogram figures to match paper order of appearence and the table ordering.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Peer-to-Peer (\p) Overlay Architectures}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Circa 2000, the first file-sharing \p-system introduced the \emph{servent}
concept~\cite{gnutella}, a \emph{portmanteau} that blends the notions of server
and client to denote the dual role of a node participating in the \p-network. 
Such server-less systems have proven to be able to achieve outstanding
aggregate resource capacities as more and more participants join the system
without requiring additional expenditure for infrastructure. 
While certain undesirable features such as 
free-riding~\cite{saroiu_measurefileshare_2002,adar_gnutellafreeriders_2000,hughes_gnutellafreeride_2005},
the distribution of illegal content and other~\emph{socio-technical}
issues \cite{hughes_socp2p_2008}, have arisen, \p\ systems have
continued to gain popularity throughout the years primarily 
because they have successfully supported popular applications 
(i.e. file-sharing) amongst \emph{vast} numbers of participating users.
%%
For over a decade, excitement over the immense potential of \p\ systems has
generated a flurry of research and development, resulting in a wide range of
popular protocols, networks, and applications. As \p\ systems evolved, three
main architectures have emerged, namely
\begin{inparaenum}[\itshape i\upshape)]
  \item \emph{centralized},
  \item \emph{decentralized unstructured}, and
  \item \emph{decentralized structured}.
\end{inparaenum}

Designers of \emph{centralized} architectures 
(Figure~\ref{figure:p2p-archs:centralized}) were the first 
to observe that requests for resources
(e.g., CPU cycles or popular content) need not be sent to
a dedicated server. Instead, such requests could be handled by 
many hosts that already possessed the resources in question. 
The downside of this approach was that it required a 
centralized search directory that invevitably becames a single point of failure,
a scalability bottleneck or a target of malicious behavior such as \emph{DoS}
attacks.

@@

Architectures that distributed both search and resource provision 
capabilities (Figure~\ref{figure:p2p-archs:unstructred-full}) soon followed.
In these \emph{decentralized} approaches, 
resource placement within the overlay topology is random~\cite{YG-M2002};
for this reason, such architectures are referred to as \emph{unstructured}. 
Key properties of such \p\ systems are that they support inherent heterogeneity
of peers, are highly resilient to peer failures, and incur low maintenance
overhead at handling the dynamics of peer participation
\cite{stutzbach_churn_2006}. Unstructured systems are also known as 
\emph{broadcast-based} systems as they use message flooding among
peers to propagate search queries. 
In its first realization,
{\sl Gnutella}(\emph{v.0.4}) is a well-known example of the fully
decentralized unstructured approach.

A key disadvantage of the unstructured approach is that message flooding burdens
the network since queries travel within the network randomly, visiting nodes
that do not have the sought resource and thus wasting bandwidth.  
To save on bandwidth, unstructured networks typically limit how long 
a query travels within the overlay via the \emph{time-to-live} parameter
(\emph{TTL}). 
When a query is received by a node, it decreases its \emph{TTL} by one unit. 
If the \emph{TTL} has not reached zero, the node forwards the query 
to its neighbors.  Otherwise, it drops the query. 
While this approach prevents queries from visiting the entire network, it
does not guarantee that the resource of interest, (e.g., a rare recording)
will, ultimately, be found.
%%%
\begin{figure}[ht]
\centering
\subfigure[Centralized ({\sl SETI@Home} or {\sl Napster}). Peers query the centralized
entity (dotted lines) and then establish the connection to the data source.] {
  \includegraphics[scale=0.20]{img/pdf/centralized.pdf}
  \label{figure:p2p-archs:centralized}
}\qquad\qquad
\subfigure[Fully unstructured ({\sl Gnutella} \emph{v.0.4}). Data is distributed randomly,
the topology is also random and all participants are equal.] {
  \includegraphics[scale=0.20]{img/pdf/unstructured-full.pdf}
  \label{figure:p2p-archs:unstructred-full}
}\qquad\qquad
\subfigure[Hierarchical unstructured ({\sl Gnutella} \emph{v.0.6} or {\sl FastTrack}). Certain
peers (bigger circles) shoulder specific responsibilities (e.g., data
indexing).] {
  \includegraphics[scale=0.20]{img/pdf/unstructured-hierarchical.pdf}
  \label{figure:p2p-archs:unstructured-hierarchical}
}\qquad\qquad
\subfigure[Structured ({\sl Chord} and {\sl Kademlia}). 
Peers and data are placed in the overlay in a deterministic manner.] {
  \includegraphics[scale=0.20]{img/pdf/structured.pdf}
  \label{figure:p2p-archs:structured}
}
\caption{The various \p\ architectures.}
\label{figure:p2p-archs}
\end{figure}

@@

One of the major issues that defines the efficiency of 
an overlay network is its mapping to 
the underlying physical infrastructure. 
Recall, in Figure~\ref{figure:overlay} nodes $A$ and $B$ are 
on the same local network, while $C$ and $D$ are in different networks. 
The top layer represents the overlay interconnection formed by 
these four nodes at a higher level. 
Link connections there, can change as needed by 
the running environment, without any
particular constraint by the underlying physical topology. 
%%
For instance, assume nodes $A$, $B$, $C$ and $D$ being 
connected via the physical network shown in Figure~\ref{figure:phys}
in which costs are depicted in milliseconds. 
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.4]{img/pdf/example-physical.pdf}
\caption{Interconnection of nodes in the physical level.}
\label{figure:phys}
\end{figure}
%%
When peer $A$ sends a message its $D$ counterpart
and depending on the overlay configuration, 
nodes will experience different performance.
For example, in the overlay depicted in
Figure~\ref{figure:overlay-1}, the
message will traverse the following sequence of links in the physical layer
(marked with their costs): $3 \rightarrow 7 \rightarrow 1 \rightarrow 2
\rightarrow 2 \rightarrow 1 \rightarrow 7 \rightarrow 8 \rightarrow 5
\rightarrow 5 \rightarrow 4$. In the alternative overlay of
Figure~\ref{figure:overlay-2}, the path will be: $3 \rightarrow 8 \rightarrow
4$. 
The respective costs are $45 ms$ and $15 ms$.
Evidently, the second overlay is more
congruent with the underlying physical network in comparison 
to the first and, thus, is more efficient.

\begin{figure}[ht]
\centering
\subfigure[Nodes $B$ and $C$ have direct overlay connection.] {
  \includegraphics[scale=0.4]{img/pdf/example-overlay-inefficient.pdf}
  \label{figure:overlay-1}
}\qquad\qquad
\subfigure[Nodes $A$ and $D$ have direct overlay connection.] {
  \includegraphics[scale=0.4]{img/pdf/example-overlay-efficient.pdf}
  \label{figure:overlay-2}
}
\caption{Two different overlay connection configuration.}
\label{figure:overlay-confs}
\end{figure}

@@

Early overlay protocol implementations did not pay to much attention to map
optimally to the underlying network topology. {\sl Gnutella}, for example, is
considered far from scalable~\cite{ritter_gnucantscale_2001} since every peer
chooses its neighbors without any knowledge of the underlying
network, resulting in mismatch. 
Queries may be flooded over multiple paths merging in one peer 
while one of the paths would suffice.  
Moreover, peers may forward the same message to each other
before they receive the query messages from each other.
\cite{matei_mapgnutella_2002} showed that, even when $95$\% of any two nodes 
are less than $7$ hops away from each other, 
a \emph{flooding-based} {\sl Gnutella}-like algorithm 
can generate $330$TB/month in a $50,000$ node network. 
A topology mismatch can thus have a serious effect 
on Internet's router performance.

@@

The topology mismatch problem is exacerbated by the extremely large amounts of
traffic generated by highly popular \p\ applications~\cite{byl-book}.
Addressing this problem remains a fundamental challenge 
in contributing to the overall efficiency of the Internet. 
Unfortunately, topology mismatch is known to be 
an \emph{NP-Hard} problem \cite{C2000,NPBOOK}. 
There is also additional complexity due to the fact that 
end-to-end latencies demonstrate \emph{triangle inequality
violations (TIVs)} which are a consequence of the Internet's structure and
routing policies; as such, they will remain a property of the Internet 
for the foreseeable future \cite{zheng_irprtt_2005}. 
\emph{TIV}s affect both network coordinate
\cite{cox_vivaldi_2004,WSS2005} and positioning \cite{ng_gnp_2001}
systems and makes the construction of \emph{IP}-topology-aware 
overlays difficult.

Over the past several years, researchers have investigated an extensive
array of heuristic solutions to the topology mismatch problem. 
The purpose of this survey is to gather and organize 
this extensive body of produced knowledge. 
We aspire to assist the reader in better understanding the 
different approaches suggested and to accomplish this we 
present methods for both structured and unstructured distributed 
overlay networks.
We outline the respective algorithmic aspects and we categorize
the surveyed material so that pros and cons of each method
can become apparent in their context.

We employ both tabular and pictorial means to 
articulate features of the proposed methodologies and outline
both strengths and weaknesses.
To ascertain the effectiveness of each proposal, we predominantly use 
three criteria that capture the behavior of the algorithms 
discussed:
\emph{efficiency}, \emph{overhead} and \emph{scalability}.
For each of these criteria, we use a coarse-grained,
three-level, gradation to denote how well the algorithms do,
namely \emph{low}, \emph{medium} and \emph{high}.
Each criterion has its own
interpretation of the above literal values. 
\emph{Efficiency} means how well the
algorithm performs its search and topology adaptation functions. Our assessment
also considers any negative effects that might come along with the application
of the algorithm on intrinsic characteristics of the system (i.e., search scope
coverage, download performance e.t.c).
%% VM Reworked above definition for "efficiency".

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Peer-to-Peer (\p) Overlay Architectures}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Circa 2000, the first file-sharing \p-system introduced the \emph{servent}
concept~\cite{gnutella}, a \emph{portmanteau} that blends the notions of server
and client to denote the dual role of a node participating in the \p-network. 
Such server-less systems have proven to be able to achieve outstanding
aggregate resource capacities as more and more participants join the system
without requiring additional expenditure for infrastructure. 
While certain undesirable features such as 
free-riding~\cite{saroiu_measurefileshare_2002,adar_gnutellafreeriders_2000,hughes_gnutellafreeride_2005},
distribution of illegal content and other~\emph{socio-technical}
issues \cite{hughes_socp2p_2008} have arisen, \p\ systems have
continued to gain popularity throughout the years primarily 
due to their successful file-sharing applications
amongst \emph{vast} numbers of participating users.
%%
For over a decade, excitement over the immense potential of \p\ systems has
generated a flurry of research and development, resulting in a wide range of
popular protocols, networks, and applications. As \p\ systems evolved, three
main architectures have emerged, namely:
\begin{inparaenum}[\itshape i\upshape)]
  \item \emph{centralized},
  \item \emph{decentralized unstructured}, and
  \item \emph{decentralized structured}.
\end{inparaenum}

Designers of \emph{centralized} architectures 
(Figure~\ref{figure:p2p-archs:centralized}) were the first 
to observe that requests for resources
(e.g., CPU cycles or popular content) need not be sent to
a dedicated server. Instead, such requests could be handled by 
many hosts that already possessed the resources in question. 
The downside of this approach was that it required a 
centralized search directory that inevitably became 
a single point of failure, a scalability bottleneck or 
a target of malicious behavior such as \emph{DoS} attacks.

@@

Architectures that distributed both search and resource provision 
capabilities (Figure~\ref{figure:p2p-archs:unstructred-full}) soon followed.
In these \emph{decentralized} approaches, 
resource placement within the overlay topology is random~\cite{YG-M2002};
for this reason, such architectures are referred to as \emph{unstructured}. 
Key properties of such \p\ systems are that they support inherent heterogeneity
of peers, are highly resilient to peer failures, and incur low maintenance
overhead at handling the dynamics of peer participation
\cite{stutzbach_churn_2006}. 
Unstructured systems are also known as 
\emph{broadcast-based} systems for they use message flooding among %% it is FOR!
peers to propagate search queries. 
In its first realization,
{\sl Gnutella}(\emph{v.0.4}) became a well-known example of the fully
decentralized unstructured approach.

A key disadvantage of the unstructured approach is that message flooding burdens
the network since queries travel within the network randomly, visiting nodes
that do not have the sought resource and thus wasting bandwidth.  
To save on bandwidth, unstructured networks typically limit how long 
a query travels within the overlay via the \emph{time-to-live} parameter
(\emph{TTL}). 
When a query is received by a node, it decreases its \emph{TTL} by one unit. 
If the \emph{TTL} has not reached zero, the node forwards the query 
to its neighbors.  Otherwise, it drops the query. 
While this approach prevents queries from visiting the entire network, it
does not guarantee that the resource of interest, (e.g., a rare recording)
will, ultimately, be found.
%%%
\begin{figure}[ht]
\centering
\subfigure[Centralized ({\sl SETI@Home} or {\sl Napster}). Peers query the centralized
entity (dotted lines) and then establish the connection to the data source.] {
  \includegraphics[scale=0.17]{img/pdf/centralized.pdf}
  \label{figure:p2p-archs:centralized}
}\qquad\qquad
\subfigure[Fully unstructured ({\sl Gnutella} \emph{v.0.4}). Data is distributed randomly,
the topology is also random and all participants are equal.] {
  \includegraphics[scale=0.17]{img/pdf/unstructured-full.pdf}
  \label{figure:p2p-archs:unstructred-full}
}\qquad\qquad
\subfigure[Hierarchical unstructured ({\sl Gnutella} \emph{v.0.6} or {\sl FastTrack}). Certain
peers (bigger circles) shoulder specific responsibilities (e.g., data
indexing).] {
  \includegraphics[scale=0.16]{img/pdf/unstructured-hierarchical.pdf}
  \label{figure:p2p-archs:unstructured-hierarchical}
}\qquad%\qquad
\subfigure[Structured ({\sl Chord}~\cite{stoica_chord_2001} and {\sl Kademlia}~\cite{maymounkov_kademlia_2002}). 
Peers and data are placed in the overlay in a deterministic manner.] {
  \includegraphics[scale=0.17]{img/pdf/structured.pdf}
  \label{figure:p2p-archs:structured}
}
\caption{The various \p\ architectures.}
\label{figure:p2p-archs}
\end{figure}

@@

One of the major issues that defines the efficiency of 
an overlay network is its mapping to 
the underlying physical infrastructure. 
Recall, in Figure~\ref{figure:overlay} nodes $A$ and $B$ are 
on the same local network, while $C$ and $D$ are in different networks. 
The top layer represents the overlay interconnection formed by 
these four nodes at a higher level. 
Link connections there, can change as needed by 
the running environment, without any
particular constraint by the underlying physical topology. 
%%
For instance, assume nodes $A$, $B$, $C$ and $D$ being 
connected via the physical network shown in Figure~\ref{figure:phys}
in which costs are depicted in milliseconds. 
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.36]{img/pdf/example-physical.pdf}
\caption{Interconnection of nodes in the physical level.}
\label{figure:phys}
\end{figure}
%%
When peer $A$ sends a message its $D$ counterpart
and depending on the overlay configuration, 
nodes will experience different performance.
For example, in the overlay depicted in
Figure~\ref{figure:overlay-1}, the
message will traverse the following sequence of links in the physical layer
(marked with their costs): $3 \rightarrow 7 \rightarrow 1 \rightarrow 2
\rightarrow 2 \rightarrow 1 \rightarrow 7 \rightarrow 8 \rightarrow 5
\rightarrow 5 \rightarrow 4$. In the alternative overlay of
Figure~\ref{figure:overlay-2}, the path will be: $3 \rightarrow 8 \rightarrow
4$. 
The respective costs are $45 ms$ and $15 ms$.
Evidently, the second overlay is more
congruent with the underlying physical network in comparison 
to the first and, thus, is more efficient.

\begin{figure}[ht]
\centering
\subfigure[Nodes $B$ and $C$ have direct overlay connection.] {
  \includegraphics[scale=0.28]{img/pdf/example-overlay-inefficient.pdf}
  \label{figure:overlay-1}
}\qquad\qquad
\subfigure[Nodes $A$ and $D$ have direct overlay connection.] {
  \includegraphics[scale=0.28]{img/pdf/example-overlay-efficient.pdf}
  \label{figure:overlay-2}
}
\caption{Two different overlay connection configuration.}
\label{figure:overlay-confs}
\end{figure}

@@

Early overlay protocol implementations did not pay much attention to map
optimally to the underlying network topology. {\sl Gnutella}, for example, is
considered far from scalable~\cite{ritter_gnucantscale_2001} for every peer
chooses its neighbors without any knowledge of the underlying
network, resulting in mismatches. 
Queries are flooded over multiple paths in an effort 
to reach the node(s) having the sought content. 
In addition, 
pairs of nodes may simultaneously forward the same query to each other
in a superflous mode of operation in 
this opportunistic and without coordination environment.
%%
\cite{matei_mapgnutella_2002} showed that, even when $95$\% of any two nodes 
are less than $7$ hops away from each other, 
a \emph{flooding-based} {\sl Gnutella}-like algorithm 
can generate $330$TB/month traffic in a $50,000$ node network. 
A topology mismatch can thus have a serious effect 
on Internet's routing performance.

@@

The topology mismatch problem is exacerbated by the extremely large amounts of
traffic generated by highly popular \p\ applications~\cite{byl-book}.
Addressing this problem remains a fundamental challenge 
in contributing to the overall efficiency of the Internet. 
Unfortunately, topology mismatch is known to be 
an \emph{NP-Hard} problem \cite{C2000,NPBOOK}. 
There is also additional complexity due to the fact that 
end-to-end latencies demonstrate \emph{triangle inequality
violations (TIVs)} which are a consequence of the Internet's structure and
routing policies; as such, they will remain a property of the Internet 
for the foreseeable future \cite{zheng_irprtt_2005}. 
\emph{TIV}s affect both network coordinate
\cite{cox_vivaldi_2004,WSS2005} and positioning \cite{ng_gnp_2001}
systems and make the construction of \emph{IP}-topology-aware 
overlays difficult.

Over the past several years, researchers have investigated an extensive
array of heuristic solutions to the topology mismatch problem. 
The purpose of this survey is to gather and organize 
this extensive body of produced knowledge. 
We aspire to assist the reader in better understanding the 
different approaches suggested and to accomplish this, we 
present methods for both structured and unstructured distributed 
overlay networks.
We outline the respective algorithmic aspects and we categorize
the surveyed material so that pros and cons of each method
can become apparent in their context.

We employ both tabular and pictorial means to 
articulate features of the proposed methodologies and outline
both strengths and weaknesses.
To ascertain the effectiveness of each proposal, we predominantly use 
three criteria that capture the behavior of the algorithms 
discussed:
\emph{efficiency}, \emph{overhead} and \emph{scalability}.
For each of these criteria, we use a coarse-grained,
three-level, gradation to denote how well the algorithms do,
namely, \emph{low}, \emph{medium} and \emph{high}.
Each criterion has its own
interpretation of the above literal values. 
\emph{Efficiency} means how well the
algorithm performs its search and topology adaptation functions. Our assessment
also considers any negative effects that might come along with the application
of the algorithm on intrinsic characteristics of the system (i.e., search scope
coverage, download performance etc.).

### 2015-05-17 conclusion.tex
2015.05.16 (Alex & Vassilis) Extensive re-wording throughout the paper. Abstract on its one file. Better figure scaling and alignment. Re-ordering of algorithms in the histogram figures to match paper order of appearence and the table ordering.

Research and development in application systems that follow the 
\p\ architectural paradigm have flourished for more than a decade now.
By and large, such systems exploit the loose-coupling and self-organization 
of participating nodes to shape substrates upon which diverse applications 
can run; the latter offer services including, but not limited to, 
distributed naming, 
Internet telephony and video conferencing, 
storage and indexing, 
content and file sharing, 
web crawling and caching, 
event notification and subscribing/publishing.
%%
These services are provided atop the 
best-effort infrastructure of today's Internet 
and they have to effectively deal with an array of key quality attributes that
they may have to offer, such as node availability, robustness,
scalability, load-sharing, quality-of-service and user anonymity.
%%
The difficulty to handle such features effectively, emanates from the fact that
peer nodes operate at the edge of the Internet and no adequate attention 
is paid to the structure of the physical network during the 
network formation at the application-level.
The deviation of the distributed logically-formed overlay from the 
physical network yields suboptimal use of the underlying 
infrastructure and is known as the topology mismatch
problem.

Development of \p--systems and applications
typically involve juggling a set of tradeoffs (e.g.,
choosing higher accuracy at the cost of increased system overhead).
% Computer systems design is typically about juggling a set of tradeoffs (e.g.,
% choosing higher accuracy at the cost of increased system overhead.)  
In surveying more than
a decade's worth of research efforts aimed at solving the topology mismatch
problem in both unstructured and structured \p\ networks, we find this
tussle-of-tradeoffs property to hold.  
With regards to the three criteria we used --efficiency,
overhead, and scalability-- we find that none of the proposed solutions 
is superior to the others on all three fronts.  This is not surprising.
Nonetheless, by
\begin{inparaenum}[\itshape i\upshape)]
  \item presenting an analysis of each of the solutions,
including what distinguishes it from 
others as well as its advantages and disadvantages and 
  \item offering a pictorial
comparison of how each solution fares in regards to others as far as
efficiency, overhead, and scalability are concerned,
\end{inparaenum}
we hope to have provided \p\
developers and researchers with enough insight and perspective;
as they face specific problems, they will be readily able to 
draw the best possible design decisions for their own application
environments.
%%AD let's avoids "giants" etc...

>>>>

Research and development in applications and systems that follow the 
\p\ architectural paradigm have flourished for more than a decade now.
By and large, such artifacts exploit the loose-coupling and self-organization 
of participating nodes to shape substrates upon which diverse applications 
can run; the latter offer services including, but not limited to, 
distributed naming, 
Internet telephony and video conferencing, 
storage and indexing, 
content and file sharing, 
web crawling and caching, 
event notification and subscribing/publishing.
%%
These services are provided atop the 
best-effort infrastructure of today's Internet 
and they have to effectively deal with an array of key quality attributes that
they may have to offer, such as node availability, robustness,
scalability, load-sharing, quality-of-service and user anonymity.
%%
The difficulty to handle such features effectively, emanates from the fact that
peer nodes operate at the edge of the Internet and no adequate attention 
is paid to the structure of the physical network during the 
network formation at the application-level.
The deviation of the distributed logically-formed overlay from the 
physical network yields suboptimal use of the underlying 
infrastructure and is known as the topology mismatch
problem.

Development of \p--systems and applications
typically involve juggling a set of tradeoffs (e.g.,
choosing higher accuracy at the cost of increased system overhead).
% Computer systems design is typically about juggling a set of tradeoffs (e.g.,
% choosing higher accuracy at the cost of increased system overhead.)  
In surveying more than
a decade's worth of research efforts aimed at solving the topology mismatch
problem in both unstructured and structured \p\ networks, we find this
tussle-of-tradeoffs property to hold.  
With regards to the three criteria we used --efficiency,
overhead, and scalability-- we find that none of the proposed solutions 
is superior to the others on all three fronts.  This is not surprising.
Nonetheless, by
\begin{inparaenum}[\itshape i\upshape)]
  \item presenting an analysis of each of the solutions,
including what distinguishes it from 
others as well as its advantages and disadvantages and 
  \item offering a pictorial
comparison of how each solution fares in regards to others as far as
efficiency, overhead, and scalability are concerned,
\end{inparaenum}
we hope to have provided \p\
developers and researchers with enough insight and perspective;
as they face specific problems, they will be readily able to 
draw the best possible design decisions for their own application
environments.

### 2015-05-17 intro.tex
2015.05.16 (Alex & Vassilis) Extensive re-wording throughout the paper. Abstract on its one file. Better figure scaling and alignment. Re-ordering of algorithms in the histogram figures to match paper order of appearence and the table ordering.

The peer-to-peer paradigm gave impetus to two ``killer'' applications:
file-sharing and Internet telephony.
The {\sl Napster} file-sharing system was widely acknowledged as the 
``fastest growing Internet application ever'' in $2001$ when it topped
$26$ million users sharing over $80$ million songs.
Other file-sharing applications followed suit, 
including {\sl Gnutella} and {\sl Limewire} enjoying $3$ 
million concurrently-connected peers, as well as 
{\sl BitTorrent} connecting over $150$ million monthly users by January $2012$~\cite{bittorrentusers}.
\p\ telephony saw explosive growth with the advent of {\sl Skype}.
Since its introduction in $2003$,
{\sl Skype} has become extremely popular with more than $650$ million users 
in $2011$~\cite{skypetotalusers}, an astonishing $50$+ million concurrently-online
users~\cite{skypesymusers} and slowly but steadily replacing traditional
carrier traffic for services like telephony services, which was recently estimated to
have reached 214 billion minutes for year 2013~\cite{skypetraffic}.

@@

\p\ systems are implemented using \emph{overlay networks}. 
An overlay network, is a virtual system of nodes and logical links
created above an existing network; overlays provide an abstraction that
enables the implementation of efficient, fully distributed, application-layer
services such as routing messages to destinations that are not known in advance
or offering QoS guarantees (i.e., in content-distribution) over best effort
infrastructures. Overlay nodes communicate through \emph{virtual connections}
each of which may correspond to a path of possibly many physical links 
in the underlying network.
Figure~\ref{figure:overlay} illustrates a simple four-node overlay constructed
over a wide-area network.
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.53]{img/pdf/under-over-lay.pdf}
\caption{An example overlay network.}
\label{figure:overlay}
\end{figure}

The single key issue that determines the efficiency of an overlay network,
is how well the overlay maps to the underlying network topology on which it
``rests''. 
Consider two nodes\footnote{In \p\ networks,
the participating nodes are typically user-PCs operating at the edge of the
Internet.} that are connected with each other via a path of overlay links.
If the application running on the nodes, generates heavy traffic along
the overlay path, it would be beneficial to
construct the overlay topology in a way that the number of 
underlying IP links between these two nodes is minimized.
Should the overlay network be constructed so that
it does not match the underlying topology well, 
the inherent \emph{topology mismatch} gives two
significant problems. First, the performance of the application per se, can be
adversely affected since traffic must flow over a larger,
redundant, number of physical hops resulting in poor user experience 
entailing noticeable latencies or jittering. 
%%
Second, other applications running
on the underlying network infrastructure are also adversely affected.
Studies have shown that highly popular \p\ applications contribute 
the largest portion of the overall 
Internet traffic~\cite{seroiu_analysiscds_2002,sen_analyzep2ptraffic_2004,krp_ispfear_2005}, with some reporting that more than $60$\% of this traffic 
to be \p-related~\cite{cachelogic,ipoque2009};
it was also projected that this traffic would reach
$7$~\emph{Exabytes}-per-month by $2018$~\cite{CVNI2014}! 
Evidently, this constitutes a major burden for 
Internet Service Providers (ISPs) who must route 
all of this traffic to destinations at the edge of the Internet. 
If the \p\ overlay topology is poorly designed, 
the demand on the Internet's backbone infrastructure may 
substantially increase as traffic might have to flow
``back and forth'' several times between two neighboring ISPs
while trying to travel from the source to its destination node
in the overlay.
Hence, it is critical that \p\ networks be laid out 
in ways that their topology matches, as closely as possible, the 
underlying IP topology.

For over a decade, researchers have extensively investigated  
various aspects of the topology mismatch problem.
The main objective of this paper is to offer a comprehensive 
survey of the work done in this and provide a
taxonomy of the proposed solutions. We point out synergies, as well as
similarities and differences in the published approaches. 
Ultimately, our goal is to help readers sift through 
the voluminous literature, to help them
understand the advantages and disadvantages of each work, and 
to provide them with enough perspective so that 
when the need arises, they are able to
select, amongst the different approaches, the one that is most suitable for
their particular application.
%%
The rest of the paper is organized as follows: 
Section~\ref{section:background} provides background on
overlay architectures including centralized, decentralized-unstructured and
decentralized-structured \p\ systems.
We also formally define the problem of topology mismatch 
and offer the rationale behind our 
evaluation of the techniques discussed in this paper. 
Sections~\ref{section:unstructured} and~\ref{section:structured}
respectively outline the surveyed research efforts 
for decentralized-unstructured and decentralized-structured \p\ systems.
Conclusions can be found in Section~\ref{section:conclusion}.

>>>>

The peer-to-peer paradigm gave impetus to two ``killer'' applications:
file-sharing and Internet telephony.
The {\sl Napster} file-sharing system was widely acknowledged as the 
``fastest growing Internet application ever'' in $2001$ when it topped
$26$ million users sharing over $80$ million songs.
Other file-sharing applications followed suit, 
including {\sl Gnutella} and {\sl Limewire} enjoying $3$ 
million concurrently-connected peers, as well as 
{\sl BitTorrent} connecting over $150$ million monthly users by January $2012$~\cite{bittorrentusers}.
\p\ telephony saw explosive growth with the advent of {\sl Skype}.
Since its introduction in $2003$,
{\sl Skype} has become extremely popular with more than $650$ million users 
in $2011$~\cite{skypetotalusers} and an astonishing 
$50$+ million concurrently-online users~\cite{skypesymusers}.
Moreover, it has consistently eroded  the traffic handled by 
traditional telephony carriers by slicing away a staggering 
$214$ billion minutes of pertinent traffic in $2013$ alone~\cite{skypetraffic}.

@@

\p\ systems are implemented using \emph{overlay networks}. 
An overlay network, is a virtual system of nodes featuring logical interconnects (or links)
created above an existing network; overlays provide an abstraction that
enables the implementation of efficient, fully distributed, application-layer
services such as routing messages to destinations that are not known in advance
or offering QoS guarantees (i.e., in content-distribution) over best effort
infrastructures. Overlay nodes communicate through \emph{virtual connections}
each of which may correspond to a path of possibly many physical links 
in the underlying network.
Figure~\ref{figure:overlay} illustrates a simple four-node overlay constructed
over a wide-area network.
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.45]{img/pdf/under-over-lay.pdf}
\caption{An example overlay network.}
\label{figure:overlay}
\end{figure}

The single key issue that determines the efficiency of an overlay network,
is how well the overlay maps to the underlying network topology on which it
``rests''. 
Consider two nodes\footnote{In \p\ networks,
the participating nodes are typically user-PCs operating at the edge of the
Internet.} that are connected with each other via a path of overlay links.
If the application running on the nodes, generates heavy traffic along
the overlay path, it would be beneficial to
construct the overlay topology in a way that the number of 
underlying IP links between these two nodes is minimized.
Should the overlay network be constructed so that
it does not match the underlying topology well, 
the inherent \emph{topology mismatch} gives two
major problems. 
First, the performance of the application per se, can be
adversely affected since traffic must flow over a larger,
redundant, number of physical hops resulting in poor user experience 
entailing noticeable latencies or jittering. 
%%
Second, other applications running
on the underlying network infrastructure may be adversely affected as well.
Studies have shown that highly popular \p\ applications contribute 
the largest portion of the overall 
Internet traffic~\cite{seroiu_analysiscds_2002,sen_analyzep2ptraffic_2004,krp_ispfear_2005}, with some reporting that more than $60$\% of this traffic 
to be \p-related~\cite{cachelogic,ipoque2009};
it was also projected that this traffic would reach
$7$~\emph{Exabytes}-per-month by $2018$~\cite{CVNI2014}! 
Evidently, this constitutes a major burden for 
Internet Service Providers (ISPs) who must route 
all of this traffic to destinations at the edge of the Internet. 
If the \p\ overlay topology is poorly designed, 
the demand on the Internet's backbone infrastructure may 
substantially increase as traffic might have to flow
``back and forth'' several times between two neighboring ISPs
while trying to travel from the source to its destination node
in the overlay.
Hence, it is critical that \p\ networks be laid out 
in ways that their topology matches, as closely as possible, the 
underlying IP topology.

For over a decade, researchers have extensively investigated  
various aspects of the topology mismatch problem.
The main objective of this paper is to offer a comprehensive 
survey of the work carried out in the area
and provide a
taxonomy of the proposed solutions. We point out synergies, as well as
similarities and differences in the published approaches. 
Ultimately, our goal is to help readers sift through 
the voluminous literature, to help them
understand the advantages and disadvantages of each work, and 
to provide them with enough perspective so that 
when the need arises, they are able to
select, amongst the different approaches, the one that is most suitable for
their particular application.
%%
The rest of the paper is organized as follows: 
Section~\ref{section:background} provides background on
overlay architectures including centralized, decentralized-unstructured and
decentralized-structured \p\ systems.
We also formally define the problem of topology mismatch 
and offer the rationale behind our 
evaluation of the techniques discussed in this paper. 
Sections~\ref{section:unstructured} and~\ref{section:structured}
respectively outline the surveyed research efforts 
for decentralized-unstructured and decentralized-structured \p\ systems.
Conclusions can be found in Section~\ref{section:conclusion}.
